\section{Introduction}\label{sec:introduction}

These notes compile my journey of learning German through a combination of self-study and formal education at the Official School of Languages (Escuela Oficial de Idiomas) in Zaragoza, Spain. They represent a blend of classroom instruction and independent learning, organized to help fellow German language learners.

The content combines standard coursework material with additional insights, tips, and explanations I've gathered through my personal study methods. While these notes align with the curriculum of the Official School of Languages, they also incorporate supplementary resources and learning strategies that I found particularly helpful during my self-study sessions.

Please note that these materials, while comprehensive, reflect my personal learning experience and understanding of the German language. Any errors or misinterpretations are my own, and I encourage readers to verify information with official sources when in doubt.

Feel free to use these notes as a complementary resource in your German language learning journey. {\em Viel Glück!} (Good luck!)

\subsection{Document Structure}

Document follows:

\begin{itemize}
    \item Section \ref{sec:preliminary}: Preliminary. This section introduces preliminary concepts necessary to understand certain parts of the document, as they will be taken for granted in the rest of the document.
    \item Section \ref{sec:pronunciation}: Pronunciation. This section explains the pronunciation of the german words.
\end{itemize}