\subsection{Activities You Do (Aktivitäten, die du machst)}\label{subsec:activities}

Some examples of questions to ask for someone activities:

\translation{Was machst du gern am Wochenende?}{\\What do you like to do at weekend?}
\translation{Kochst du gern?}{Do you like cooking?}
\translation{Gehst du gern ins Kino?}{Do you like going to the cinema?}
\translation{Liest du gern?}{Do you like reading?}
\translation{Schwimmst du gern?}{Do you like swimming?}
\translation{Tanzt du gern?}{Do you like dancing?}
\translation{Reist du gern?}{Do you like traveling?}
\translation{Singst du gern?}{Do you like singing?}
\translation{Jaggst du gern?}{Do you like running (as an sport)?}
\translation{Fotografierst du gern?}{Do you like photographing?}
\translation{Hörst du gern Musik?}{Do you like listening to music?}

Some answers to express your likes:

\translation{Ich schwimme gern samstags morgens}{\\I like to swimming Saturday mornings}
\translation{Ich gehe gern sonnstags ins Kino}{\\I like going to the cinema on Saturdays}

Some answers for the previous questions to answer if you like something or not:

\translation{Gern}{I like it}
\translation{Nicht gern}{I don't like it}
\translation{Es geht so}{It's okay, so-so}
\translation{Sehr gern}{I like it a lot}
\translation{Nicht so gern}{I don't like to much}

Some activities of interest are listed in Table \ref{tab:activities}.

\begin{table}[H]
    \centering
    \begin{tabular}{c|c}
    \hline
    \textbf{Aktivität} & \textbf{Activity} \\
    \hline
    fotografieren & to phorograph \\
    singen & to sign\\
    kochen & to cook\\
    schwimmen & to swim\\
    reisen & to travel (enjoy)\\
    fahren & to travel (work)\\
    tanzen & to dance\\
    joggen & to running (as an sport)\\
    Music hören & to listen to music\\
    ins Kino gehen & to go to the cinema\\
    lessen & to read\\
    \hline
    \end{tabular}
    \caption{List of activities to do with their translation}
    \label{tab:activities}
\end{table}